Comparing Facebook Prophet Forecasts to those of an ARIMA Model

### 2017-09-14 template/Draft_Paper.Rmd
corrected notation in draft paper(P_t)

In this paper, the **log return**(which will be used interchangeably with **return**), over the period $[t,t+1]$ is denoted by $r_t$, and was calculated by evaluating;  
$$
r_t = log(\frac{P_{t+1}}{P_t})  \label{eq1}
$$  
Where $P_{t+1}$ and $P_{t+1}$ represent the price of the index at time $t$ and $t+1$ respectively.

>>>>

In this paper, the **log return**(which will be used interchangeably with **return**), over the period $[t,t+1]$ is denoted by $r_t$, and was calculated by evaluating;  
$$
r_t = log(\frac{P_{t+1}}{P_t})  \label{eq1}
$$  
Where $P_t$ and $P_{t+1}$ represent the price of the index at time $t$ and $t+1$ respectively.
